---
title: "Element showcase"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Element showcase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/CTTIR/themakR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CTTIR/themakR/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/CTTIR/themakR/actions/workflows/pkgdown.yaml/badge.svg)](https://cttir.github.io/themakR/)
[![CRAN status](https://www.r-pkg.org/badges/version/themakR)](https://CRAN.R-project.org/package=themakR)
[![Codecov test coverage](https://codecov.io/gh/CTTIR/themakR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/CTTIR/themakR?branch=main)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/themakR)](https://cran.r-project.org/package=themakR)
[![CRAN downloads total](https://cranlogs.r-pkg.org/badges/grand-total/themakR)](https://cran.r-project.org/package=themakR)
[![License: MIT](https://img.shields.io/badge/license-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4.5,
  dpi = 96,
  warning = FALSE,
  message = FALSE
)
has_ggplot2 <- requireNamespace("ggplot2", quietly = TRUE)
```

This page renders one of every styled element so the theme can be checked
visually in both light and dark mode. Use the toggle at the top right.

## Heading level two

Body copy set in Inter. Here is a [link to the CTTIR site](https://cttir.github.io/website/),
some **bold text**, some *italic text*, and inline code such as
`pkgdown::build_site()` or `x <- c(1, 2, 3)` set in JetBrains Mono.

### Heading level three

#### Heading level four

## Code

A fenced, evaluated R chunk with output:

```{r demo-code}
fib <- function(n) {
  if (n < 2) return(n)
  fib(n - 1) + fib(n - 2)
}
vapply(0:10, fib, numeric(1))
```

And a static YAML block:

```yaml
template:
  package: themakR
  bslib:
    primary: "#1565c0"
```

## Table

```{r demo-table, echo = FALSE}
knitr::kable(
  head(mtcars[, 1:6]),
  caption = "The first rows of mtcars."
)
```

## Blockquote

> The accent is restrained: it colours links, active navigation, focus rings,
> and the hex border — never large fills.

## Lists

1. An ordered item
2. Another ordered item

- An unordered item with `inline code`
- Another unordered item

## Figure

```{r demo-plot, eval = has_ggplot2, echo = has_ggplot2}
library(ggplot2)
ggplot(mpg, aes(displ, hwy)) +
  geom_point(colour = "#1565c0", alpha = 0.7) +
  geom_smooth(method = "loess", formula = y ~ x, colour = "#212121") +
  labs(
    title = "Engine displacement vs. highway mileage",
    x = "Displacement (litres)", y = "Highway miles per gallon"
  ) +
  theme_minimal(base_size = 12)
```

## Math

KaTeX rendering: when $a \ne 0$, the roots of $ax^2 + bx + c = 0$ are

$$x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}.$$
